For testing OurBiCopSelect.R

### 2018-02-13 Test_OurBiCopSelect.Rmd
small changes

<!--Source in the function and a package, changeable constants-->
```{r}
source("OurBiCopSelect.R")
require(copula)
nbsmall<-8
pthresh<-0.2
nblarge<-15 #for bootstrapping, see below
numdat<-100 #amount of artificial data
```

@@

If real data come from a Clayton copula, independence should
be rejected, Clayton should be the AIC best, it should pass the
goodness of fit test, and the normal copula should fail the
goodness of fit test:
<!--Test for real data from a clayton-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,mtime("OutBiCopSelect.R"))}
families<-c(1,3:6,13,14,16)

@@

Same test, but data now come from a Gumbel copula:
<!--Test for real data from a gumbel-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,mtime("OutBiCopSelect.R"))}
#data are really from a gumbel
cop<-gumbelCopula(4,2)
dat<-rCopula(numdat,cop)
allresG<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresG
```

Same test, but data now come from a Frank copula:
<!--Test for real data from a frank-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,mtime("OutBiCopSelect.R"))}
#data are really from a frank
cop<-frankCopula(5,2)
dat<-rCopula(numdat,cop)
allresF<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresF
```

>>>>

<!--Source in the function and a package, changeable constants-->
```{r}
source("OurBiCopSelect.R")
require(copula)
nbsmall<-100
pthresh<-0.2
nblarge<-1000 #for bootstrapping, see below
numdat<-500 #amount of artificial data
seed<-101
```

@@

If real data come from a Clayton copula, independence should
be rejected, Clayton should be the AIC best, it should pass the
goodness of fit test, and the normal copula should fail the
goodness of fit test:
<!--Test for real data from a clayton-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

families<-c(1,3:6,13,14,16)

@@

Same test, but data now come from a Gumbel copula:
<!--Test for real data from a gumbel-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

#data are really from a gumbel
cop<-gumbelCopula(6,2)
dat<-rCopula(numdat,cop)
allresG<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresG
```

Same test, but data now come from a Frank copula:
<!--Test for real data from a frank-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

#data are really from a frank
cop<-frankCopula(5,2)
dat<-rCopula(numdat,cop)
allresF<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresF
```

Same test, but data now come from a Joe copula:
<!--Test for real data from a joe-->
```{r cache=T, cache.extra=list(nbsmall,nblarge,pthresh,numdat,seed,mtime("OurBiCopSelect.R"))}
set.seed(seed)

#data are really from a joe
cop<-joeCopula(6,2)
dat<-rCopula(numdat,cop)
allresJ<-OurBiCopSelect(dat[,1],dat[,2],families,numBSsmall=nbsmall,
                        numBSlarge=nblarge,pthresh=0.2)
allresJ
```
